RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-26 manuscripts/manuscript.Rmd
re-flow paragraph
request for clarification
removed duplicate comment delimiter

Note that the `add_namespaces` function will automatically avoid creating
any duplicate definitions.

For finer control of the level at which a `meta` element is added,
we will manipulate the nexml R object directly using S4 subsetting,
as shown later.

<!--FIXME Ugh. y'all have much more practice explaining this well and without tangents, 
so please feel free to edit or re-write.  -->

@@

<!--  Find more consise way to make sure dependencies are cited. 
      How about citing packages that are only on the suggests list? --> 
--> 
<!-- Possibly cite all dependencies and suggests from the DESCRIPTION --> 
<!-- Reference any installation and configuration instructions necessary (e.g. API credentials for figshare) -->

>>>>

Note that the `add_namespaces` function will automatically avoid creating
any duplicate definitions. 
For finer control of the level at which a `meta` element is added,
we will manipulate the nexml R object directly using S4 subsetting,
as shown later.

<!--FIXME Ugh. y'all have much more practice explaining this well and without tangents, 
so please feel free to edit or re-write.  -->
<!-- I am not quite sure what points we are trying to make here -->

@@

<!--  Find more consise way to make sure dependencies are cited. 
      How about citing packages that are only on the suggests list? --> 
<!-- Possibly cite all dependencies and suggests from the DESCRIPTION --> 
<!-- Reference any installation and configuration instructions necessary (e.g. API credentials for figshare) -->
